Choose a License

### 2024-11-28 choose_license.qmd
Fix typo

---
title: "Choose a License"
lang: en
engine: knitr
---

@@

@@

::: {#wrn-exclusive-rights .callout-warning}
### Giving Publishers Exclusive Rights

@@

::: {.column-margin}
If you would like to choose a license not listed here, it should be appropriate for the type of work in question and be compatible with the dominant copyleft license in the respective community (see also @nte-silos). For software that's almost universally the (A)GPLv3 and for writing, image, audio, and video that's mostly the [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/). For data, no dominant copyleft license has emerged yet, so any of [ODbL\ 1.0](https://opendatacommons.org/licenses/odbl/summary/), [CDLA\ Sharing\ 1.0](https://cdla.dev/sharing-1-0/), and [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/) are acceptable.
:::

@@

One should take special care when applying license to the following types of works:

@@

  subgraph "License for combination of data (database)"
  choose_license --> switch_license["<em>Depending on<br>content license</em>"]
  use_existing_license_content --> switch_license

>>>>

---
title: "Choose a License"
lang: en
format:
  html:
    mermaid:
      theme: neutral
engine: knitr
---

@@

::: {#nte-situation-lmu .callout-note collapse="true"}
### For researchers at LMU

If you are an employee at LMU and your funder does not mandate the use of a particular license, the decision which license to use lies with your associated chair. In the (rare) case the software you developed has a technical application and it falls under the legal definition of an invention, you are required to officially report your invention to the university which decides on its release. If the university claims the invention, you may not apply a copyright license that makes a patent grant. In all other cases you are free to license your research project as you like.

More information about the invention disclosure process can be found in the [service portal](https://www.serviceportal.verwaltung.uni-muenchen.de/internationals/research_transfer/intellectual_property/index.html). More information about software patents are provided by the FSFE: [Software Patents in Europe](https://fsfe.org/activities/swpat/swpat.en.html).
:::

@@

::: {#cau-exclusive-rights .callout-caution}
### Giving Publishers Exclusive Rights

@@

::: {.column-margin}
If you would like to choose a license not listed here, it should be appropriate for the type of work in question and be compatible with the dominant copyleft license in the respective community (see also @nte-silos). For software that's almost universally the (A)GPLv3 and for writing, image, audio, and video that's mostly the CC\ BY-SA\ 4.0. For data, no dominant copyleft license has emerged yet, so any of [ODbL\ 1.0](https://opendatacommons.org/licenses/odbl/summary/), [CDLA\ Sharing\ 1.0](https://cdla.dev/sharing-1-0/), and CC\ BY-SA\ 4.0 are acceptable.
:::

@@

One should be cautious about the restrictions of licenses applied to the following types of works:

@@

  subgraph "License for combination of data (database)"
  choose_license --> switch_license["<em>Depending on content license</em>"]
  use_existing_license_content --> switch_license
